The manageability of pollination networks in an invasion context

### 2017-02-25 paper/supp_info_2.Rmd
Add authors

---
title: "Biotic invasions fuck with the manageability of pollination networks"
subtitle: "Supporting Information"
classoption: a4paper
csl: ecology-letters.csl
output:
  bookdown::pdf_document2:
    fig_crop: no
    keep_tex: yes
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \renewcommand{\thefigure}{S\arabic{figure}}
- \renewcommand{\thetable}{S\arabic{table}}
- \usepackage{booktabs}
- \usepackage[tableposition=top]{caption} 
documentclass: artikel1
bibliography: references.bib
nocite: | 
  @Lopezaraiza-Mikel2007, @Bartomeus2008
---

>>>>

---
title: "The manageability of pollination networks in an invasion context"
subtitle: "Supporting Information"
author: "E. Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: ecology-letters.csl
output:
  bookdown::pdf_document2:
    fig_crop: no
    keep_tex: yes
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \renewcommand{\thefigure}{S\arabic{figure}}
- \renewcommand{\thetable}{S\arabic{table}}
- \usepackage{booktabs}
- \usepackage[tableposition=top]{caption} 
documentclass: artikel1
bibliography: references.bib
nocite: | 
  @Lopezaraiza-Mikel2007, @Bartomeus2008
---
